Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 be.tex
appendix B4

Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with
the result of equation \eqref{eq:Phi}, we obtain
\begin{align}
  &\mathcal{B} = -U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)}
  \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}
where $U_o=4 \pi G \rhostar(\rs) \rs^2$.  We may rewrite this as

\begin{multline}
  \mathcal{B} =\frac{G \Mbh}{\rs} \biggl[ \frac{3}{2} \zeta^2
  w^{\frac{1}{3 -\delta}}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2
    -\delta} -w
  \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1} \biggr],
\label{eq:enthAnal}
\end{multline}
where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv
(\rs/\rsoi)^{3\delta}$, and $\delta$ is the power law slope of the
stellar density profile inside of the break radius, $\rb$.

When the rate of external heating is high, we have $\mathcal{B} > 0$
at all radii, requiring an outflow.  As heating ($\zeta$) is
decreased, there exists a critical value of $\zeta = \zeta_{c}$ below
which $\mathcal{B}$ first becomes negative.  If $\zeta<\zeta_c$, then
there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$,
above which we have $\mathcal{B} > 0$ at the break radius, allowing an
outflow with positive kinetic energy at infinity.  The value of
$\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a
greater heating rate is required to unbind gas from a deeper stellar
potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find
$\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the
top panel of Fig.~\ref{fig:zetaCrit}). Likewise $(r_{\rm
  s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$,
approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right
  numbers here}.  For values of $\zeta<\zeta_c$, the stagnation radius
rapidly approaches the break radius as shown in the bottom panel of
Fig.~\ref{fig:zetaCrit}.

>>>>

Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with
the result of equation \eqref{eq:Phi}, we obtain
\begin{align}
  &\mathcal{B} = -U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)}
  \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}
where $U_o=4 \pi G \rhostar|_{\rs} \rs^2$.  This can be rewritten as
\begin{multline}
  \mathcal{B} =\frac{G \Mbh}{\rs} \biggl[ \frac{3}{2} \zeta^2
  w^{\frac{1}{3 -\delta}}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2
    -\delta} -w
  \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1} \biggr],
\label{eq:enthAnal}
\end{multline}
where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv
(\rs/\rsoi)^{3\delta}$, and $\delta$ is the power law slope of the
stellar density profile inside of the break radius, $\rb$.

Analysis of equation (\ref{eq:enthAnal}) results in the following.  When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow.  As $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative, first near the stagnation radius and then at larger radii as $\zeta$ is reduced further.  If $\zeta<\zeta_c$, then we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.

The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
Fig.~\ref{fig:zetaCrit} for the case of core galaxies). Likewise $(r_{\rm s,min}/r_{b})$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.86\zeta_c$, as shown in the
bottom panel of Fig.~\ref{fig:zetaCrit}.  In practice, as $\zeta \rightarrow 0.86\zeta_c$ we find that the stagnation radius moves its value predicted by equations (\ref{eq:stag_analytic}), (\ref{eq:densSlope}) to the break radius.
